Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-31 doc/paper/paper.tex
minor changes

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  m..m # m..m # m..m # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  M..m # M..m # M..m # m..m # M..m # ...m # ..m. # ..m. # ..m. # ...m # ...m # ...M # ..M. # ..M. # .... #
  .... # .... # .... # M..m # ...m # ...M # ..M. # ..M. # ..M. # ...M # ...M # .... # .... # .... # .... #
  .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... # .... #
  ..A. # .A.. # A... # A... # A... # A... # A... # .A.. # ..A. # ..A. # ...A # ...A # ...A # ..A. # ..A. #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  A..... # ...... # ...... # ...... # ...... # ...... # .....T # ....AT #
  ...... # .A.... # .A.... # ...... # .....T # ...A.T # ...A.. # ...... #
  ...... # ...... # .....T # ..A..T # ..A... # ...... # ...... # ...... #
  .....T # .....T # ...... # ...... # ...... # ...... # ...... # ...... #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
.  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Atom[holding_pet] [k=1]
  (B) Dist[cell-has-pet;adjacent_cell;cell-has-agent] [k=4]
  (C) Dist[cell-has-destiny;adjacent_cell;cell-has-agent] [k=4
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
p.... # p.... # .p... # .p... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
  .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  Q  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  K  .  k  #  .  .  .  .  .  .  .  K  .  k  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  .  .  R  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  R  #
  .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
\end{Verbatim}

>>>>

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
    # m.mm.m # m.mm.m # m.mm.m # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # m.mm.m # m.mm.m # m.mm.. # m.mm.m # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.mm. # ..m.mm #
    # m.mm.m # m.mm.. # m.mm.. # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.mm. # .m.m.. # ..m.m. #
    # ...... # ...... # ...... # m.mm.. # m.mm.. # m.mm.. # .m.mm. # .m.m.. # .m.m.. # ..m.m. #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # .....A # .....A # .....A # .....A # .....A # ....A. # ....A. # ....A. # ....A. # ....A. # ...

    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ..m.mm # ..m.mm # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ..m.m. # ..m... # ..m.mm # ..m..m # ..m..m # ...... # ...... # ...... # ...... # ...... #
    # ..m... # ..m... # ..m... # ..m... # ..m... # ..m..m # ..m... # ..m... # ...m.. # ...m.. #
    # ...... # ...... # ..m... # ..m... # ..m... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
    # ...... # ...... # ...... # ...... # ...... # ..m... # ..m... # ..m... # ...m.. # ...m.. #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
... # ....A. # ....A. # ....A. # ....A. # .....A # .....A # .....A # ....A. # ....A. # ...A.. # ...

    # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... #
    # ...m.. # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... #
    # ...m.. # ...m.. # ...m.. # ...... #
    # ...... # ...m.. # ...... # ...... #
    # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... #
    # ...... # ...... # ...... # ...... #
... # ...A.. # ...A.. # ...A.. # ...A.. #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
 # A..... # ...... # ...... # ...... # ...... # ...... # .....T # ....AT #
 # ...... # .A.... # .A.... # ...... # .....T # ...A.T # ...A.. # ...... #
 # .....T # .....T # ...... # ...... # ...... # ...... # ...... # ...... #
 # ...... # ...... # .....T # ..A..T # ..A... # ...... # ...... # ...... #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
 # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #  .  .  #  .  .  #
 # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #  .  .  #  .  .  #
 # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
 # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
 # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
 # t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  t  #  t  .  #  .  .  #
\end{Verbatim}

@@

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Atom[holding_pet] [k=1]
  (B) Dist[cell-has-pet;adjacent_cell;cell-has-agent] [k=4]
  (C) Dist[cell-has-destiny;adjacent_cell;cell-has-agent] [k=4]
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
 # p.... # p.... # .p... # .p... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... #
 # ..... # ..... # A.... # ..... # ..... # ..... # ..... # ..A.. # .pA.. # ..A.. # ..... # ..... # ..... #
 # ..... # ..... # ..... # .A... # .A... # pA... # .A... # ..... # ..... # ..... # ..... # ..... # ..... #
 # ..... # .A... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ..... # ...A. # ..... # ..... #
 # A...D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....D # ....A # ....A #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  K  .  .  #  .  .  .  .  .  .  .  K  .  .  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  .  .  k  #  .  .  .  .  .  .  .  .  Q  k  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  Q  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
   # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
\end{Verbatim}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  K  .  k  #  .  .  .  .  .  .  .  K  .  k  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
  # .  .  R  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  R  #
  # .  .  .  .  .  .  .  .  .  .  #  .  .  .  .  .  .  .  .  .  .  #
\end{Verbatim}
